\sysfull

### 2018-08-04 paper/asplos19/coalescing.tex
revise WEG algo

\subsubsection{Weighted History-Guided Coalescing (WHG)}

@@

The Weighted History-Guided (WHG) coalescing strategy accounts for the

@@

The EO and HG coalescing strategies assume each task has uniform energy cost:

@@

Instead, WHG associates a non-unity weight with each task in the program. 
%
WHG tracks the sum of the weights of tasks in a coalesced sequence of tasks.
%
When the sum of weights reaches $B$, the target, WHG commits the coalesced
task.
%
WHG differs extends EO and HG to explicitly account for the variation in energy
cost of a program's tasks, eliminating the assumption that all tasks do the
same work, which is a key limitation.
%
WHG has the same characteristic operations as HG, except that
$f_\text{weight}(T_\text{i}) = W_\text{i}$.

The effectiveness of the WHG algorithm hinges on correctly identifying the
weight of each task, which WHG assumes is {\em statically} available.
%
Profiling the time and energy cost of tasks in a program is a difficult,
orthogonal problem~\cite{cleancut_2018,baghsorkhi_cgo_2018}.
%
WHG could use the result of an arbitrarily sophisticated profiling procedure.
%
To produce a concrete result in this paper, we give WHG access to a simple
profile of task run time collected offline using a single fixed input.
%
WHG stores the profile in a lookup table that maps a task's identifier to its
weight, making the information available to \sys's scheduler at run time.

>>>>

\subsubsection{Weighted Energy-Guided Coalescing (WEG)}

@@

The \emph{Weighted Energy-Guided} (WEG) coalescing strategy accounts for the

@@

The EO and EG coalescing strategies assume each task has uniform energy cost:

@@

Instead, WEG associates a non-unity weight with each task in the program. 
%
WEG tracks the sum of the weights of tasks in a coalesced sequence of tasks.
%
When the sum of weights reaches $B$, the target, WEG commits the coalesced
task.
%
WEG differs from EO and HG by explicitly accounting for the variation in energy
cost of a program's tasks, eliminating the assumption that all tasks do the
same work, which is a key limitation.
%
WEG has the same characteristic operations as HG, except that
$f_\text{weight}(T_\text{i}) = W_\text{i}$.

The effectiveness of the WEG algorithm hinges on correctly identifying the
weight of each task, which WEG assumes is {\em statically} available.
%
Profiling the time and energy cost of tasks in a program is a difficult,
orthogonal problem~\cite{cleancut_2018,baghsorkhi_cgo_2018}.
%
WEG could use the result of an arbitrarily sophisticated profiling procedure.
%
To produce a concrete result in this paper, we give WEG access to a simple
profile of task run time collected offline using a single fixed input.
%
WEG stores the profile in a lookup table that maps a task's identifier to its
weight, making the information available to \sys's scheduler at run time.
